An umbrella review of the benefits and risks associated with youths' interactions with electronic screens

### 2023-06-20 reports/manuscript.Rmd
Update abstract

abstract: |
  The influence of electronic screens on children and adolescents’ health and education is not well understood.
  In this review, we harmonised `r targets::tar_read(manuscript_info)$unique_effects` effects representing unique combinations of exposures and outcomes from `r targets::tar_read(manuscript_info)$prisma$unique_reviews` meta-analyses (`r format(targets::tar_read(manuscript_info)$effects_sum$sum_k, big.mark=",")` primary studies; `r format(targets::tar_read(manuscript_info)$effects_sum$sum_n, big.mark=",")` participants).
  Some types of screen use, such as social media, were consistently correlated with risks to health.
  However, other forms of screen use showed associations with benefits.
  For example, educational screen use was generally associted with better learning outcomes.
  Some types of screen use have complex associations with outcomes.
  For example, television viewing showed harmful correlations with body composition and learning.
  However, when parents watched with their children or the content was educational, general screen use was associated with greater learning.
  More nuanced guidelines are needed to help parents, teachers, and practitioners ensure that youth benefit from their interactions with screens.

@@

options(dplyr.summarise.inform = FALSE)
```

```{r, load-targets}
targets::tar_load(
  c(
    "manuscript_info", "combined_bib", "prisma", "edu_certain_params",
    "plot_edu_certain", "nonedu_certain_params", "plot_nonedu_certain"
  ),
  store = here::here("_targets")
)
```

@@

As shown in Figure 2, most of the credible results (`r manuscript_info$edu$n_p999` of `r manuscript_info$edu$n_certain` effects) showed statistically significant associations, with 99.9\% confidence intervals not encompassing zero (strong evidence).
The remaining `r xfun::numbers_to_words(manuscript_info$edu$n_p95)` associations were significant at the 95% confidence level (weak evidence).
All credible effects related to education outcomes were small-to-moderate.
Screen-based interventions designed to influence an outcome (e.g., a computer based program designed to enhance learning [@xieCanTouchscreenDevices2018]) tended to have larger effect sizes than exposures that were not specifically intended to influence any of the measured outcomes (e.g., the association between television viewing and learning [@adelantado-renauAssociationScreenMedia2019]).
The largest effect size observed was for augmented reality-based education interventions on general learning ($r = 0.33, k = 15, N = 1,474$).
Most effects showed high levels of heterogeneity (`r manuscript_info$edu$n_i2` of `r manuscript_info$edu$n_certain` with $I^2 > 50\%$).

@@

Across the health outcomes, most (`r manuscript_info$health$n_p999` of `r manuscript_info$health$n_certain`) effects were statistically significant at the 99.9\% confidence interval level, with the remaining `r xfun::numbers_to_words(manuscript_info$health$n_p95)` significant at 95\% confidence.
However, most of the credible effects exhibited high levels of heterogeneity, with all but two having $I^2 > 75\%$.
Additionally, most effects were small, with the association between internet use and depression the largest at $r = 0.25$ ($k = 118, N = 527,696$).
Most of the effect sizes (`r manuscript_info$health$n_r2`/`r manuscript_info$health$n_certain`) had an absolute value of $r < 0.2$.

>>>>

abstract: |
  The influence of electronic screens on children and adolescents’ health and education is not well understood.
  In this prospectively registered umbrella review (PROSPERO; CRD42017076051), we harmonised effects from `r targets::tar_read(manuscript_info)$prisma$unique_reviews` meta-analyses (`r format(targets::tar_read(manuscript_info)$effects_sum$sum_k, big.mark=",")` primary studies; `r format(targets::tar_read(manuscript_info)$effects_sum$sum_n, big.mark=",")` participants) on screen time and any outcome for youths.
  Some types of screen use, such as social media, were consistently correlated with risks (e.g., depression, `r targets::tar_read(manuscript_info)$abstract$social_media`) while others, such as educational screen use, showed associations with benefits (e.g., motivation for learning, `r targets::tar_read(manuscript_info)$abstract$edu`).
  Some types of screen use have complex associations with outcomes.
  For example, television viewing showed harmful correlations with learning `r targets::tar_read(manuscript_info)$abstract$tv_edu`.
  However, when parents watched with their children, general screen use was associated with greater literacy `r targets::tar_read(manuscript_info)$abstract$coview`.
  These findings suggest that caregivers need to carefully weigh the pros and cons of each specific activity for potential harms and benefits.

@@

options(dplyr.summarise.inform = FALSE)

source(here::here("R", "utils_manuscript.R"))
```

```{r, load-targets}
targets::tar_load(
  c("manuscript_info", "combined_bib", "combined_effects"),
  store = here::here("_targets")
)
```

@@

As shown in Figure 2, most of the credible results (`r manuscript_info$edu$n_p999` of `r manuscript_info$edu$n_certain` effects) showed statistically significant associations, with 99.9\% confidence intervals not encompassing zero (strong evidence).
The remaining `r xfun::numbers_to_words(manuscript_info$edu$n_p95)` associations were significant at the 95% confidence level (weak evidence).
All credible effects related to education outcomes were small-to-moderate.
Screen-based interventions designed to influence an outcome (e.g., a computer based program designed to enhance learning [@xieCanTouchscreenDevices2018]) tended to have larger effect sizes than exposures that were not specifically intended to influence any of the measured outcomes (e.g., the association between television viewing and learning [@adelantado-renauAssociationScreenMedia2019]).
The largest effect size observed was for augmented reality-based education interventions on general learning `r report_effect(combined_effects, "42168_002")`.
Most effects showed high levels of heterogeneity (`r manuscript_info$edu$n_i2` of `r manuscript_info$edu$n_certain` with $I^2 > 50\%$).

@@

Across the health outcomes, most (`r manuscript_info$health$n_p999` of `r manuscript_info$health$n_certain`) effects were statistically significant at the 99.9\% confidence interval level, with the remaining `r xfun::numbers_to_words(manuscript_info$health$n_p95)` significant at 95\% confidence.
However, most of the credible effects exhibited high levels of heterogeneity, with all but two having $I^2 > 75\%$.
Additionally, most effects were small, with the association between internet use and depression the largest at `r report_effect(combined_effects, "60496_003", "in-text")`.
Most of the effect sizes (`r manuscript_info$health$n_r2`/`r manuscript_info$health$n_certain`) had an absolute value of $r < 0.2$.

### 2023-06-20 reports/manuscript.tex
Update abstract

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{\newline\indent Word count: 5405}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

@@

\abstract{%
The influence of electronic screens on children and adolescents' health and education is not well understood.
In this review, we harmonised 255 effects representing unique combinations of exposures and outcomes from 103 meta-analyses (2,496 primary studies; 2,026,054 participants).
Some types of screen use, such as social media, were consistently correlated with risks to health.
However, other forms of screen use showed associations with benefits.
For example, educational screen use was generally associted with better learning outcomes.
Some types of screen use have complex associations with outcomes.
For example, television viewing showed harmful correlations with body composition and learning.
However, when parents watched with their children or the content was educational, general screen use was associated with greater learning.
More nuanced guidelines are needed to help parents, teachers, and practitioners ensure that youth benefit from their interactions with screens.
}

@@

As shown in Figure 2, most of the credible results (14 of 23 effects) showed statistically significant associations, with 99.9\% confidence intervals not encompassing zero (strong evidence).
The remaining six associations were significant at the 95\% confidence level (weak evidence).
All credible effects related to education outcomes were small-to-moderate.
Screen-based interventions designed to influence an outcome (e.g., a computer based program designed to enhance learning\textsuperscript{26}) tended to have larger effect sizes than exposures that were not specifically intended to influence any of the measured outcomes (e.g., the association between television viewing and learning\textsuperscript{27}).
The largest effect size observed was for augmented reality-based education interventions on general learning (\(r = 0.33, k = 15, N = 1,474\)).
Most effects showed high levels of heterogeneity (18 of 23 with \(I^2 > 50\%\)).

@@

Across the health outcomes, most (14 of 21) effects were statistically significant at the 99.9\% confidence interval level, with the remaining four significant at 95\% confidence.
However, most of the credible effects exhibited high levels of heterogeneity, with all but two having \(I^2 > 75\%\).
Additionally, most effects were small, with the association between internet use and depression the largest at \(r = 0.25\) (\(k = 118, N = 527,696\)).
Most of the effect sizes (17/21) had an absolute value of \(r < 0.2\).

>>>>

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{\newline\indent Word count: 5377}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

@@

\abstract{%
The influence of electronic screens on children and adolescents' health and education is not well understood.
In this prospectively registered umbrella review (PROSPERO; CRD42017076051), we harmonised effects from 103 meta-analyses (2,496 primary studies; 2,026,054 participants) on screen time and any outcome for youths.
Some types of screen use, such as social media, were consistently correlated with risks (e.g., depression, \emph{r} = 0.12, 95\% confidence interval 0.05 to 0.19) while others, such as educational screen use, showed associations with benefits (e.g., motivation for learning, \emph{r} = 0.16, 95\% confidence interval 0.02 to 0.31).
Some types of screen use have complex associations with outcomes.
For example, television viewing showed harmful correlations with learning (\emph{r} = -0.10, 95\% confidence interval -0.15 to -0.04).
However, when parents watched with their children, general screen use was associated with greater literacy (\emph{r} = 0.15, 95\% confidence interval 0.02 to 0.28).
These findings suggest that caregivers need to carefully weigh the pros and cons of each specific activity for potential harms and benefits.
}

@@

As shown in Figure 2, most of the credible results (14 of 23 effects) showed statistically significant associations, with 99.9\% confidence intervals not encompassing zero (strong evidence).
The remaining six associations were significant at the 95\% confidence level (weak evidence).
All credible effects related to education outcomes were small-to-moderate.
Screen-based interventions designed to influence an outcome (e.g., a computer based program designed to enhance learning\textsuperscript{26}) tended to have larger effect sizes than exposures that were not specifically intended to influence any of the measured outcomes (e.g., the association between television viewing and learning\textsuperscript{27}).
The largest effect size observed was for augmented reality-based education interventions on general learning (\emph{r} = 0.33, 95\% confidence interval 0.25 to 0.42, \emph{k} = 15, \emph{N} = 1,474).
Most effects showed high levels of heterogeneity (18 of 23 with \(I^2 > 50\%\)).

@@

Across the health outcomes, most (14 of 21) effects were statistically significant at the 99.9\% confidence interval level, with the remaining four significant at 95\% confidence.
However, most of the credible effects exhibited high levels of heterogeneity, with all but two having \(I^2 > 75\%\).
Additionally, most effects were small, with the association between internet use and depression the largest at \emph{r} = 0.25 (95\% confidence interval 0.22 to 0.27, \emph{k} = 118, \emph{N} = 527,696).
Most of the effect sizes (17/21) had an absolute value of \(r < 0.2\).
